Executive Constraints and Civil Conflict Onset

### 2020-08-08 paper.Rmd
Switch to Chicago style citations and add proper title page

---
title: Executive Constraints and Civil Conflict Onset
author: J.L.A. Krusell
date: "`r format(Sys.time(), '%Y-%m-%d')`"
suppress-bibliography: false
bibliography: library.bib
csl: assets/american-political-science-association.csl
link-citations: true
documentclass: scrreprt
fontsize: 11pt
linestretch: 1.5
header-includes:
    - \usepackage{amsmath}
    - \usepackage{etoolbox}
    - \usepackage{lualatex-math}
    - \usepackage{unicode-math}
    - \appto\Shaded{\singlespacing}
    - \BeforeBeginEnvironment{align*}{\begin{singlespace}\vspace*{-\baselineskip}}
    - \AfterEndEnvironment{align*}{\end{singlespace}\noindent\ignorespaces}
    - \counterwithout{table}{chapter}
    - \counterwithout{figure}{chapter}
output:
    pdf_document:
        fig_caption: true
        keep_tex: true
        latex_engine: lualatex
        toc: true
        toc_depth: 2
        pandoc_args: ["--syntax-definition", "assets/stan.xml",
                      "--highlight-style", "kate",
                      "--lua-filter", "utils/text_refs/text_refs.lua"]
    html_document:
        smart: true
        toc: true
abstract: Lorem ipsum
---

>>>>

---
title: Executive Constraints and Civil Conflict Onset
author:
    name: J.L.A. Krusell
    affiliation: Department of Peace and Conflict Research, Uppsala University
    supervisor: Kristine Eck
    degree: Master's Thesis
date: "Spring 2020"
titlelogo: |
    ```{=latex}
    assets/UU_logo_CMYK-eps-converted-to.pdf
    ```
wordcount: 13052
suppress-bibliography: false
bibliography: library.bib
csl: assets/chicago-author-date.csl
link-citations: true
documentclass: scrreprt
classoption: paper=letter
geometry:
    - top=30mm
    - heightrounded
fontsize: 11pt
linestretch: 1.5
header-includes:
    - \usepackage{amsmath}
    - \usepackage{etoolbox}
    - \usepackage{lualatex-math}
    - \usepackage{unicode-math}
    - \appto\Shaded{\singlespacing}
    - \BeforeBeginEnvironment{align*}{\begin{singlespace}\vspace*{-\baselineskip}}
    - \AfterEndEnvironment{align*}{\end{singlespace}\noindent\ignorespaces}
    - \counterwithout{table}{chapter}
    - \counterwithout{figure}{chapter}
output:
    pdf_document:
        fig_caption: true
        keep_tex: true
        latex_engine: lualatex
        toc: true
        toc_depth: 2
        pandoc_args: ["--template", "assets/thesis_template.latex",
                      "--syntax-definition", "assets/stan.xml",
                      "--highlight-style", "kate",
                      "--lua-filter", "utils/text_refs/text_refs.lua"]
    html_document:
        smart: true
        toc: true
abstract: Lorem ipsum
---
